\documentclass[12pt]{article} % Please don't change the font size!

\setlength{\textheight}{24cm}

\begin{document}

\pagestyle{empty} % we don't need a page number for a single page

\begin{center}
\section*{Hash-table report}
\end{center}

\section{Linear Probing and Double Hashing}

Two methods are used in my hash-table to calculate where a key
should be stored if a key is already in the position the new
key hashes to. Linear probing looks at the next adjacent space
in the hash table to see if that is free, wheras double hashing
creates a new hash for the key and offsets the next space it will
probe by the hash. 

Linear probing has the advantage that it is easy to calculate the
next step and is easy to implement, but has a drawback that if many
keys hash to the same value they will all be put in one after another
creating large areas where the hash table is full and empty, also 
causing alot of collisions to happen when another key is inserted
that hashes to around the same value. Double hashing gets around 
this problem by creating a different step for each key so it is 
less likely that the keys get bunched up in the hash table. This 
means collisions are less likely to happen and will therefore be
faster to insert and search keys.

Running the program on a very large text file proved this theory as 
the average number of collisions using double hashing was approximately
half of linear probing.

\section{Implementation}

My hash table implementation is very basic containing only only insert,
search and delete and able to use only linear probing and double hashing
as collision reduction techniques. It could have been improved by adding
a remove function to allow keys to be removed from the table and
implementing chaining, so if a key collides with another they are put
into a linked list containing all keys that hash to the same value. 
The size limit of the hash table could also be removed if it could
dynamically create a new hash table when the old one runs out of space,
rehashing all of the old keys into a new hash table.

\subsection*{BE VERY CAREFUL NOT TO EXCEED 1 PAGE!}

\end{document}
